Viscous Erosion in Porous Media

### 2018-03-08 docs/methods/erosion_methods.tex
Added values to GMRES table.
NM

We now consider the system of evolution equations given by \eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
\begin{align}
%\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vnsig}, \\
%\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha
\Vssig \right), \\
%\label{eq:elfun}
& \elfun = \frac{2 \pi}{L}  \mean{\atausig} \, .
\end{align}
Then, ~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = \Mterm, \\
\label{eqn:thetaevo2}
& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm.
\end{align}
The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity gives rise to a diffusive term in the tangent angle $\theta$. This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$). Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$. Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.

@@

% Table: GMRES iterations
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{GMRES Iterations
}
\vspace{0.3 pc}
\label{itertab}
\begin{tabular}{c c | c c}
\hline
\hspace{0.5pc} Number of bodies
\hspace{0.5pc} & GMRES iterations 
\hspace{0.5pc} & Resolution, $N_{\iin}$
\hspace{0.5pc} & GMRES iterations  \\
\hspace{0.0pc} ($N_\iin = 128$ fixed) & 
\hspace{0.5pc} &(10 bodies) & \\
\hline
%
10	& 223	& 32	    	& ?	\\
15	& 292	& 64    	& ?	\\
20	& 363	& 128	& ?	\\
30	& 496	& 256	& ?	\\
40	& 676	& 512	& ?	\\
50	& 991	& 1024	& ?	\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% In these tests I always use 128 points per body.

>>>>

We now consider the system of evolution equations given by \eqref{eqn:Levo1}--\eqref{eq:xsurf}. For convenience, we introduce the following variables
\begin{align}
%\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vnsig}, \\
%\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atausig}{\alpha} + \thalpha
\Vssig \right), \\
%\label{eq:elfun}
& \elfun = \frac{2 \pi}{L}  \mean{\atausig} \, .
\end{align}
Then, ~\eqref{eqn:Levo1} and~\eqref{eqn:thetaevo1} can be compactly expressed as
\begin{align}
\label{eqn:Levo2}
& \tderiv{L}{t} = \Mterm, \\
\label{eqn:thetaevo2}
& \pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm.
\end{align}
The first term on the right-hand-side of \eqref{eqn:thetaevo2} is the stiff term resulting from the curvature penalization; i.e.~a curvature-driven interface velocity is associated with diffusion of the tangent angle $\theta$. This term is multiplied by $\zeta$, which is spatially constant but depends on time (due to $L$ and $\mean{\atau}$). Meanwhile, $\NLterm$, represents all remaining terms in the evolution equation, including contributions from the shear-dependent erosion law and from the artificial tangential velocity, $\Vs$. Since the local shear stress depends on interactions between bodies, $\NLterm$ is both a nonlinear and nonlocal.

@@

% Table: GMRES iterations
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{GMRES Iterations: the tolerance is 1E-8.
}
\vspace{0.3 pc}
\label{itertab}
\begin{tabular}{c c | c c}
\hline
\hspace{0.5pc} Number of bodies
\hspace{0.5pc} & GMRES iterations 
\hspace{0.5pc} & Resolution, $N_{\iin}$
\hspace{0.5pc} & GMRES iterations  \\
\hspace{0.0pc} ($N_\iin = 128$ fixed) & 
\hspace{0.5pc} &(10 bodies) & \\
\hline
%
10	& 223	& 32	    	& 228	\\
15	& 292	& 64    	& 226	\\
20	& 363	& 128	& 223	\\
30	& 496	& 256	& 223	\\
40	& 676	& 512	& 223	\\
50	& 991	& 1024	& 223	\\
%
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% In these tests I always use 128 points per body.
